### 2017-08-08 presentations/qual/sequence.tex
[presentations/qual] Smooth out sequence plot

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, -0.3) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, -0.3) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
    }

    %% Radial 2
    \foreach \i in {0,...,3} {
      \fill[red!30]
      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4})
      -- cycle;
      \draw[line width=1,red] (5.6*\i, 0) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textit{Radial $x$}};
    \path[red] (5.6*1+2.1, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[red] (5.6*2+2.1, 0.05) node[below,align=center] {\textbf{pulse $2$}};

    %% Radial 3
    \foreach \i in {0,...,3} {
      \fill[black!30]
      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4})
      -- cycle;
      \draw[line width=1,black] (5.6*\i, 0) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textit{Radial $y$}};
    \path[black] (5.6*1+5.2, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[black] (5.6*2+5.2, 0.05) node[below,align=center] {\textbf{pulse $2$}};

>>>>

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[smooth,domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, -0.3) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, -0.3) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
    }

    %% Radial 2
    \foreach \i in {0,...,3} {
      \fill[red!30]
      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4})
      -- cycle;
      \draw[line width=1,red] (5.6*\i, 0) -- plot[smooth,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textit{Radial $x$}};
    \path[red] (5.6*1+2.1, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[red] (5.6*2+2.1, 0.05) node[below,align=center] {\textbf{pulse $2$}};

    %% Radial 3
    \foreach \i in {0,...,3} {
      \fill[black!30]
      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4})
      -- cycle;
      \draw[line width=1,black] (5.6*\i, 0) -- plot[smooth,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textit{Radial $y$}};
    \path[black] (5.6*1+5.2, 0.05) node[below,align=center] {\textbf{pulse $1$}};
    \path[black] (5.6*2+5.2, 0.05) node[below,align=center] {\textbf{pulse $2$}};
